---
title: "Conversion Prediction — First-look Baseline (v1)"
author: "Uncle May's ML"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: show
    df-print: paged
    embed-resources: true
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    geometry:
      - margin=1in
    fontsize: 10pt
    code-overflow: wrap
    fig-pos: "H"
execute:
  echo: true
  warning: false
  message: false
engine: knitr
---

```{r setup}
suppressPackageStartupMessages({
  library(arrow)
  library(dplyr)
  library(tidyr)
  library(tibble)
  library(stringr)
  library(lubridate)
  library(purrr)
  library(ggplot2)
  library(scales)
  library(knitr)

  library(tidymodels)
  library(workflowsets)
  library(themis)
  library(vip)
  library(hardhat)
})

set.seed(42)
# Note: tidymodels_prefer() omitted to dodge a fastmap version conflict on
# this machine. We disambiguate any clashing function names (filter, select)
# inline via package::fun where needed.

# Reusable feature-prep + recipe builder.
source("_feature_prep.R")
```

## 1. Load + inspect

```{r load}
df_path <- latest_parquet(dir = "../data/processed")
cat("loading:", df_path, "\n")
df_raw <- arrow::read_parquet(df_path) |> as_tibble()
cat("shape:", nrow(df_raw), "x", ncol(df_raw), "\n")
```

```{r class-balance}
df_raw |>
  count(source, label) |>
  arrange(source, label) |>
  knitr::kable(caption = "Source × label cross-tab")
```

```{r missingness}
miss_pct <- df_raw |>
  summarise(across(everything(), ~ mean(is.na(.x)))) |>
  pivot_longer(everything(), names_to = "column", values_to = "pct_missing") |>
  arrange(desc(pct_missing))

miss_pct |>
  filter(pct_missing > 0) |>
  head(30) |>
  mutate(pct_missing = scales::percent(pct_missing, accuracy = 0.1)) |>
  knitr::kable(caption = "Top-30 columns by % missing")
```

```{r attempts-per-email}
df_raw |>
  group_by(email_hash) |>
  summarise(
    attempts = n(),
    eventually_paid = max(as.integer(label)),
    .groups = "drop"
  ) |>
  count(attempts, eventually_paid) |>
  arrange(desc(attempts)) |>
  head(15) |>
  knitr::kable(caption = "Attempts-per-email distribution (top 15 buckets)")
```

> **Outlier flag:** the bucket showing several hundred attempts under a single
> `email_hash` is the anonymous (`NA`) bucket — one or more bots/probes sharing
> a null email. We cap that in step 2 below.

## 2. Clean (drop leakage, cap outlier, type-coerce)

```{r clean}
df_clean <- clean_attempts(df_raw, max_per_anon_bucket = 3, verbose = TRUE)
cat("after clean:", nrow(df_clean), "rows x", ncol(df_clean), "cols\n")
df_clean |> count(label) |> knitr::kable(caption = "Class balance after cleaning")
```

> **Important:** capping anonymous attempts dramatically changes the class
> balance because most negatives in the raw data are anonymous bot/probe
> traffic. We move from ~3% positive (raw) to ~34% positive (cleaned). This
> is a deliberate trade-off — the model now learns "what predicts conversion
> among real-looking attempts" instead of "is this anonymous traffic." Bump
> `max_per_anon_bucket` if you want to keep more of the original imbalance.

## 3. Recipes

```{r recipes}
rec_balanced <- build_recipe(df_clean, use_smote = FALSE)
rec_smote    <- build_recipe(df_clean, use_smote = TRUE)

# Sanity-check the prepped feature matrix
prep_balanced <- prep(rec_balanced)
baked <- bake(prep_balanced, new_data = NULL)
cat("recipe-prepped:", nrow(baked), "x", ncol(baked), "cols\n")
cat("predictor cols (first 25):\n")
cat(paste(" -", head(setdiff(names(baked), "label"), 25)), sep = "\n")
```

## 4. Models

For the **balanced** run we add `scale_pos_weight = neg/pos` to XGBoost and
`class.weights` to ranger. glmnet (logistic) gets observation `case_weights`
via the workflow. SMOTE versions skip these and let synthetic resampling
balance the recipe output.

```{r weights}
n_pos <- sum(df_clean$label == "1")
n_neg <- sum(df_clean$label == "0")
pos_weight <- n_neg / max(n_pos, 1)
cat("n_pos:", n_pos, " n_neg:", n_neg, " pos_weight:", round(pos_weight, 2), "\n")
```

```{r model-specs}
spec_lr <- logistic_reg(penalty = 0.01, mixture = 1) |>
  set_engine("glmnet") |>
  set_mode("classification")

spec_rf_balanced <- rand_forest(trees = 500, min_n = 5) |>
  set_engine(
    "ranger",
    importance = "permutation",
    class.weights = c("0" = 1, "1" = pos_weight)
  ) |>
  set_mode("classification")

spec_rf_smote <- rand_forest(trees = 500, min_n = 5) |>
  set_engine("ranger", importance = "permutation") |>
  set_mode("classification")

spec_xgb_balanced <- boost_tree(
  trees = 500,
  learn_rate = 0.05,
  tree_depth = 4
) |>
  set_engine("xgboost", scale_pos_weight = pos_weight) |>
  set_mode("classification")

spec_xgb_smote <- boost_tree(
  trees = 500,
  learn_rate = 0.05,
  tree_depth = 4
) |>
  set_engine("xgboost") |>
  set_mode("classification")
```

## 5. Cross-validation + fit

```{r cv}
folds <- vfold_cv(df_clean, v = 5, strata = label)

metrics <- metric_set(yardstick::pr_auc, yardstick::roc_auc, yardstick::brier_class)

ctrl <- control_resamples(save_pred = TRUE, allow_par = FALSE)
```

### 5a. Manual per-model fits

Fitting each (model × resampling) combo individually so we can see exactly
which combo fails (workflow_set hides this). Six fits total: 3 models × 2
resampling strategies.

```{r fits}
safe_fit <- function(spec, rec, folds, metrics, ctrl) {
  wf <- workflow() |> add_recipe(rec) |> add_model(spec)
  res <- tryCatch(
    fit_resamples(wf, resamples = folds, metrics = metrics, control = ctrl),
    error = function(e) {
      cat("[fit FAILED]:", conditionMessage(e), "\n")
      NULL
    }
  )
  res
}

run_specs <- list(
  list(model = "lr",  resampling = "balanced", spec = spec_lr,           rec = rec_balanced),
  list(model = "rf",  resampling = "balanced", spec = spec_rf_balanced,  rec = rec_balanced),
  list(model = "xgb", resampling = "balanced", spec = spec_xgb_balanced, rec = rec_balanced),
  list(model = "lr",  resampling = "smote",    spec = spec_lr,           rec = rec_smote),
  list(model = "rf",  resampling = "smote",    spec = spec_rf_smote,     rec = rec_smote),
  list(model = "xgb", resampling = "smote",    spec = spec_xgb_smote,    rec = rec_smote)
)

results_list <- lapply(run_specs, function(s) {
  cat("- fitting:", s$model, s$resampling, "...\n")
  res <- safe_fit(s$spec, s$rec, folds, metrics, ctrl)
  list(model = s$model, resampling = s$resampling, result = res)
})
```

## 6. Headline metrics table

```{r headline}
collect_one <- function(item) {
  na_row <- tibble(model = item$model, resampling = item$resampling,
                   .metric = c("pr_auc", "roc_auc", "brier_class"),
                   mean = NA_real_, std_err = NA_real_, n = 0L)
  if (is.null(item$result)) return(na_row)
  m <- tryCatch(collect_metrics(item$result), error = function(e) NULL)
  if (is.null(m) || nrow(m) == 0) {
    cat("[collect FAILED]:", item$model, item$resampling,
        "- all folds errored. Run show_notes() on item$result to see why.\n")
    return(na_row)
  }
  m |>
    dplyr::filter(.metric %in% c("pr_auc", "roc_auc", "brier_class")) |>
    dplyr::select(.metric, mean, std_err, n) |>
    dplyr::mutate(model = item$model, resampling = item$resampling, .before = 1)
}

headline_full <- purrr::map_dfr(results_list, collect_one) |>
  pivot_wider(
    names_from = .metric,
    values_from = c(mean, std_err)
  ) |>
  dplyr::select(
    model, resampling,
    pr_auc = mean_pr_auc, pr_auc_se = std_err_pr_auc,
    roc_auc = mean_roc_auc, roc_auc_se = std_err_roc_auc,
    brier = mean_brier_class
  ) |>
  dplyr::arrange(dplyr::desc(pr_auc))

floor_pr_auc <- mean(df_clean$label == "1")

cat("majority-baseline PR-AUC floor (= class prior):",
    round(floor_pr_auc, 4), "\n\n")

headline_full |>
  dplyr::mutate(dplyr::across(where(is.numeric), ~ round(.x, 3))) |>
  knitr::kable(caption = "Headline metrics: 5-fold stratified CV")
```

## 7. Variable importance

```{r vip-fits}
fit_for_importance <- function(spec, rec) {
  workflow() |>
    add_recipe(rec) |>
    add_model(spec) |>
    fit(data = df_clean)
}

# Use the BALANCED variants for importance to keep apples-to-apples; we'll
# just look at which features each model thinks matter most.
fit_lr  <- fit_for_importance(spec_lr,           rec_balanced)
fit_rf  <- fit_for_importance(spec_rf_balanced,  rec_balanced)
fit_xgb <- fit_for_importance(spec_xgb_balanced, rec_balanced)
```

```{r vip-plots, fig.width=10, fig.height=5}
p_lr  <- vip(extract_fit_engine(fit_lr),  num_features = 15) + ggtitle("LR (|coef|)")
p_rf  <- vip(extract_fit_engine(fit_rf),  num_features = 15) + ggtitle("RF (permutation)")
p_xgb <- vip(extract_fit_engine(fit_xgb), num_features = 15) + ggtitle("XGBoost (gain)")

print(p_lr)
print(p_rf)
print(p_xgb)
```

## 8. Summary

```{r summary}
best_row <- headline_full |> slice_max(pr_auc, n = 1)

# Consensus top features across the three models (intersect of top-10 by importance)
top_features_one <- function(fit, n = 10) {
  vi <- vi(extract_fit_engine(fit))
  if (nrow(vi) == 0) return(character(0))
  vi |> arrange(desc(abs(Importance))) |> head(n) |> pull(Variable)
}

top_lr  <- top_features_one(fit_lr,  10)
top_rf  <- top_features_one(fit_rf,  10)
top_xgb <- top_features_one(fit_xgb, 10)

consensus <- Reduce(intersect, list(top_lr, top_rf, top_xgb))
two_of_three <- unique(c(
  intersect(top_lr, top_rf),
  intersect(top_lr, top_xgb),
  intersect(top_rf, top_xgb)
))
```

```{r summary-print, results="asis"}
cat("### Best model\n\n")
cat("- ", best_row$model, " (", best_row$resampling, ")\n", sep = "")
cat("- PR-AUC: ", round(best_row$pr_auc, 3),
    " ± ", round(best_row$pr_auc_se, 3),
    " (floor = ", round(floor_pr_auc, 3), ")\n", sep = "")
cat("- ROC-AUC: ", round(best_row$roc_auc, 3),
    " ± ", round(best_row$roc_auc_se, 3), "\n\n", sep = "")

cat("### SMOTE verdict\n\n")
balanced_best <- headline_full |> filter(resampling == "balanced") |>
  slice_max(pr_auc, n = 1)
smote_best <- headline_full |> filter(resampling == "smote") |>
  slice_max(pr_auc, n = 1)
delta <- smote_best$pr_auc - balanced_best$pr_auc
verdict <- if (is.na(delta)) "n/a" else if (delta > 0.02) "SMOTE helped" else if (delta < -0.02) "SMOTE hurt" else "neutral"
cat("- balanced best PR-AUC: ", round(balanced_best$pr_auc, 3), "\n", sep = "")
cat("- SMOTE best PR-AUC:    ", round(smote_best$pr_auc, 3), "\n", sep = "")
cat("- delta: ", round(delta, 3), "  →  **", verdict, "**\n\n", sep = "")

cat("### Consensus top features (top-10 across LR, RF, XGB)\n\n")
if (length(consensus) > 0) {
  for (f in consensus) cat("- ", f, "\n", sep = "")
} else {
  cat("- No features in all three top-10s. ",
      "2-of-3 agreement: ",
      paste(two_of_three, collapse = ", "), "\n", sep = "")
}

cat("\n### Recommendations\n\n")
cat("- N=", nrow(df_clean), " with ", n_pos, " positives is too thin for a deployable model. ",
    "Treat these PR-AUC numbers as ±0.05 noise.\n", sep = "")
cat("- Note: the headline numbers reflect the **cleaned** dataset ",
    "(", nrow(df_clean), " rows, base rate = ", round(floor_pr_auc, 2),
    "). The raw spine was ", nrow(df_raw), " rows; ",
    nrow(df_raw) - nrow(df_clean), " were dropped as anonymous-bucket overflow.\n", sep = "")
cat("- Re-run weekly. Custom-cart launch will inflate both row count AND ",
    "GA4 BQ join coverage (currently 1/305).\n")
cat("- Drop features that appear in ZERO importance plots.\n")
cat("- Consider instrumenting: time-on-page (Clarity), scroll depth (GA4 once cart launches), ",
    "ad-click-to-checkout latency (Meta CAPI).\n")
```
