---
title: "Conversion-Prediction Baseline — Deployment Readiness Assessment"
subtitle: "Model Card v1.0 | UNC-768"
author: "ML Engineer, Uncle May's"
date: "2026-05-03"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: show
    df-print: paged
    embed-resources: true
    theme: flatly
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    geometry:
      - margin=1in
    fontsize: 10pt
    code-overflow: wrap
    fig-pos: "H"
execute:
  echo: false
  warning: false
  message: false
engine: knitr
---

```{r setup, include=FALSE}
suppressPackageStartupMessages({
  library(arrow)
  library(dplyr)
  library(tidyr)
  library(tibble)
  library(lubridate)
  library(knitr)
  library(scales)
})
```

---

## Executive Summary

> **Verdict: NOT READY FOR PRODUCTION.**
> The conversion-prediction prototype in `01_first_look_baseline.qmd` is a
> well-structured research notebook, not a deployable system. There is no
> serialized model artifact, no serving API, no monitoring, and no retraining
> loop. The training dataset (305 rows, ≈10 real positives before anon-capping)
> is too small to produce estimates with confidence intervals narrower than ±0.05
> AUC. The correct near-term decision is to **continue collecting data and
> investing in attribution coverage** before deploying to any real decision
> (ad bidding, personalization, or segmentation).

This document:

1. Summarizes the prototype as built
2. Scores it against a deployment readiness checklist
3. Ranks the gaps that must be closed before production use
4. Maps the data dependencies the model requires

---

## 1. Model Summary

### 1.1 Business Question

> *Given a checkout attempt (a Stripe Checkout Session or PaymentIntent), what
> is the probability that this customer completes payment?*

Intended applications: abandon-recovery prioritization, ad-bid adjustment,
customer segmentation. **None of these applications are live yet.**

### 1.2 Architecture

The prototype evaluates **six (model × resampling) combinations** via 5-fold
stratified cross-validation:

| Model | Engine | Resampling | Imbalance handling |
|-------|--------|------------|-------------------|
| Logistic Regression (L1) | glmnet (R) | Balanced | `case_weights` via workflow |
| Random Forest | ranger (R) | Balanced | `class.weights = c(0=1, 1=pos_weight)` |
| XGBoost | xgboost (R) | Balanced | `scale_pos_weight = neg/pos` |
| Logistic Regression (L1) | glmnet (R) | SMOTE | synthetic minority oversampling |
| Random Forest | ranger (R) | SMOTE | synthetic minority oversampling |
| XGBoost | xgboost (R) | SMOTE | synthetic minority oversampling |

Hyperparameters are fixed (not tuned): LR penalty = 0.01, RF trees = 500,
XGB trees = 500 / lr = 0.05 / depth = 4. No hyperparameter search has been run.

### 1.3 Training Data

```{r load-parquet}
# Load the latest processed parquet for static statistics.
processed_dir <- "../data/processed"
files <- list.files(processed_dir,
                    pattern = "^conversion_v2_.*\\.parquet$",
                    full.names = TRUE)
latest_file <- sort(files, decreasing = TRUE)[1]

df_raw <- tryCatch(
  arrow::read_parquet(latest_file) |> as_tibble(),
  error = function(e) NULL
)
```

```{r data-stats, results="asis"}
if (!is.null(df_raw)) {
  n_rows   <- nrow(df_raw)
  n_cols   <- ncol(df_raw)
  n_pos    <- sum(df_raw$label == 1, na.rm = TRUE)
  n_neg    <- sum(df_raw$label == 0, na.rm = TRUE)
  base_rate_raw <- n_pos / n_rows
  n_email_non_null <- sum(!is.na(df_raw$email_hash))
  file_ts  <- basename(latest_file)

  cat("| Metric | Value |\n")
  cat("|--------|-------|\n")
  cat("| Source parquet | `", file_ts, "` |\n", sep = "")
  cat("| Total rows (raw spine) | ", scales::comma(n_rows), " |\n", sep = "")
  cat("| Columns | ", n_cols, " |\n", sep = "")
  cat("| Positive class (converted) | ", n_pos, " |\n", sep = "")
  cat("| Negative class (abandoned) | ", n_neg, " |\n", sep = "")
  cat("| Raw base rate | ", scales::percent(base_rate_raw, accuracy = 0.1), " |\n", sep = "")
  cat("| Rows with non-null email_hash | ", n_email_non_null, " |\n", sep = "")
} else {
  cat("*Parquet not found — run `python -m ml.features.build_dataset` to regenerate.*\n")
}
```

> **Why the notebook shows ~34% positive rate but the raw parquet is ~3%:**
> `clean_attempts()` in `_feature_prep.R` caps anonymous (null-email) attempts
> at 3 per fingerprint bucket, collapsing the bot/probe-dominated negative class.
> This is intentional — the model should learn "what predicts conversion among
> real-looking attempts," not "is this anonymous traffic?" The cleaning step
> is correctly designed but dramatically changes the effective dataset size.

### 1.4 Feature Space

```{r feature-list, results="asis"}
if (!is.null(df_raw)) {
  # Leakage and ID cols (from _feature_prep.R) — these are dropped before modeling.
  leakage_cols <- c("chg_status", "chg_failure_code", "chg_failure_message",
                    "chg_network_status", "chg_seller_message", "chg_outcome_type",
                    "chg_risk_level", "cs_recovery1_at", "cs_recovery2_at",
                    "cs_recovery3_at")
  id_cols <- c("attempt_id", "payment_intent_id", "email", "email_hash",
               "customer_id", "customer_name", "metadata_email", "billing_email",
               "billing_name", "client_ip", "client_user_agent", "cart_json",
               "mc_tags", "apollo_org_name", "apollo_city", "apollo_state",
               "apollo_country", "apollo_labels", "shipping_street",
               "metadata_utm_content", "metadata_utm_term", "fbc", "fbp",
               "gclid", "fbclid", "checkout_session_local_id", "line_items_summary")
  target_col <- "label"
  drop_all <- c(leakage_cols, id_cols, target_col)

  feature_cols <- setdiff(names(df_raw), drop_all)

  # Classify features by source
  classify_source <- function(col) {
    if (grepl("^mc_|^mailchimp", col)) "Mailchimp"
    else if (grepl("^resend_", col)) "Resend"
    else if (grepl("^apollo_|is_apollo", col)) "Apollo"
    else if (grepl("^ga4_|^ga_", col)) "GA4"
    else if (grepl("^cs_", col)) "Checkout Store"
    else if (grepl("^cust_", col)) "Stripe Customer"
    else if (grepl("^chg_", col)) "Stripe Charge"
    else if (grepl("^zip_|^census", col)) "Census ACS"
    else if (grepl("^meta_|has_fbclid", col)) "Meta Ads"
    else if (grepl("^gads_|has_gclid", col)) "Google Ads"
    else if (grepl("^campaign_slug", col)) "Campaign Map"
    else if (col %in% c("amount_cents", "currency", "shipping_city",
                         "shipping_state", "shipping_zip", "source",
                         "metadata_product", "metadata_utm_source",
                         "metadata_utm_medium", "metadata_utm_campaign",
                         "created_at", "created_dow", "created_hour_utc"))
      "Stripe / Core"
    else if (grepl("^attempt_|^prior_|^is_first|^seconds_since", col)) "Attempt Features"
    else "Other"
  }

  feat_df <- tibble(
    feature = feature_cols,
    source = sapply(feature_cols, classify_source)
  )

  feat_df |>
    count(source, name = "n_features") |>
    arrange(desc(n_features)) |>
    knitr::kable(caption = paste("Feature sources —", length(feature_cols),
                                  "total features (before recipe drops)"))
}
```

**Recipe transformations** (from `_feature_prep.R`):

- Log-transforms `amount_cents` and `seconds_since_prior_attempt`
- Extracts day-of-week, hour, and is-weekend from `created_at`
- Lumps rare categoricals (<2%) into "Other"
- Drops zero-variance and near-zero-variance columns
- Median-imputes numeric predictors (for glmnet compatibility)
- SMOTE applied post-recipe when `use_smote = TRUE`

### 1.5 Held-out Performance

> **Note:** The baseline notebook does not produce a held-out test-set score.
> All metrics reported below are 5-fold cross-validation estimates from
> `01_first_look_baseline.qmd`. With only ≈10–30 positives depending on
> the anon-capping threshold, each fold contains 2–6 positive examples.
> AUC estimates at this sample size have standard errors large enough that
> model comparisons are unreliable. The PR-AUC numbers should be treated
> as rough feasibility signals, not deployment thresholds.

| Metric | Interpretation | Reliability at N≈30 positives |
|--------|---------------|-------------------------------|
| ROC-AUC | Rank-ordering quality | Low (±0.10 SE expected) |
| PR-AUC | Precision-recall tradeoff | Very low (±0.10–0.15 SE) |
| Brier score | Calibration of probabilities | Low |

**Majority-class PR-AUC floor** (= base rate after anon-capping): approximately
**0.34**. Any model must beat this to add value.

The Decision Scientist's notebook summary (`section 8`) states directly:
*"N=X with Y positives is too thin for a deployable model. Treat these
PR-AUC numbers as ±0.05 noise."*

---

## 2. Deployment Readiness Checklist

```{r checklist, results="asis"}
checklist <- tribble(
  ~Category, ~Item, ~Status, ~Notes,

  "Artifact", "Serialized model file (.pkl / .joblib / .rds)",
  "MISSING", "No artifact found in `ml/models/`. Notebook trains but never saves.",

  "Artifact", "Reproducible training script (separate from notebook)",
  "MISSING", "Training logic is embedded in the Quarto notebook. No `train.py` or equivalent.",

  "Artifact", "Versioned artifact registry (S3 / GCS / MLflow)",
  "MISSING", "No registry. Local disk only.",

  "Serving", "Prediction API endpoint (REST / Trigger.dev task)",
  "MISSING", "No API. No Trigger.dev task. No R plumber service.",

  "Serving", "Batch prediction pipeline (offline scores in BQ / parquet)",
  "MISSING", "Not built.",

  "Serving", "Input validation (schema enforcement at inference time)",
  "MISSING", "No serving layer exists to validate against.",

  "Monitoring", "Score distribution drift alert",
  "MISSING", "No monitoring infrastructure exists.",

  "Monitoring", "Feature drift alert (population stability index or similar)",
  "MISSING", "Not built.",

  "Monitoring", "Ground-truth feedback loop (labels landing back to evaluate live predictions)",
  "MISSING", "Not built. Labels are only visible after Stripe resolves the attempt.",

  "Retraining", "Retraining trigger (schedule or performance threshold)",
  "MISSING", "No trigger. Retraining is manual.",

  "Retraining", "Automated pipeline to rebuild `conversion_v2` parquet and re-fit",
  "PARTIAL", "`run_pipeline.py` and `ml/ingest/*.py` exist; no orchestrated retrain schedule.",

  "Data", "Stable, versioned feature parquet produced reliably by Data Engineer",
  "PARTIAL", "Ingest scripts exist and ran on 2026-05-02. No reliability SLA or freshness alert.",

  "Data", "GA4 attribution coverage >10% (needed for GA4 features to add signal)",
  "PARTIAL", "Attribution fixed 2026-05-03 (UTM/gclid/fbclid now flow end-to-end). Historical coverage <1%. Future coverage TBD.",

  "Data", "Minimum training positives (≥100 real converters recommended)",
  "MISSING", "10 positives in raw parquet (2026-05-02). ~30 post anon-capping. Well below threshold.",

  "Governance", "Model card reviewed and approved by Decision Scientist + CEO",
  "MISSING", "This document is the first model card. Pending review (UNC-768).",

  "Governance", "Fairness check (disparate impact on protected characteristics)",
  "MISSING", "Census ACS demographic features are in the feature set. No fairness audit done.",

  "Governance", "Retraining cadence and on-call owner defined",
  "MISSING", "Not defined."
)

checklist |>
  mutate(
    Status = case_when(
      Status == "MISSING"  ~ "❌ MISSING",
      Status == "PARTIAL"  ~ "⚠️ PARTIAL",
      Status == "DONE"     ~ "✅ DONE",
      TRUE                 ~ Status
    )
  ) |>
  knitr::kable(caption = "Deployment readiness checklist — conversion prediction v1")
```

**Score: 0 / 16 items fully done, 3 partial.**

---

## 3. Gaps and Recommendations (Ranked)

Items are ranked by blocking severity: **P0** = must fix before any production
signal is used; **P1** = must fix before soft-launch to a single use case;
**P2** = should fix within 30 days of soft-launch.

### P0 — Blockers (do not deploy until resolved)

**P0-A: Training N is too small.**
10 raw positives (≈30 post anon-capping) yields cross-validation estimates
with ±0.05–0.15 AUC standard errors. Confidence intervals span most of the
meaningful range. A model trained on this data will assign scores with very
wide uncertainty, making it unsuitable for bidding or personalization.

*Recommended action:* Wait until the dataset has ≥100 real converters (not
SMOTE-augmented). At the current trajectory, this requires monitoring weekly
ingest from Stripe and re-evaluating after each weekly delivery cycle. Custom-
cart launch will accelerate this.

**P0-B: No serialized model artifact.**
Even if metrics were acceptable, there is nothing to serve. The notebook
trains models in memory and discards them at session end.

*Recommended action (when N is sufficient):* Add a `save_model()` step at the
end of the training notebook or in a standalone `ml/models/train.py` script.
For R, use `saveRDS(fit_rf, "ml/models/conv_pred_v1_rf.rds")`. For Python
portability, serialize with `joblib` after porting the winner to scikit-learn.

**P0-C: No fairness audit.**
The feature set includes Census ACS demographic proxies (income, age, household
size, racial composition by ZIP). Using these to rank customers for recovery
or bidding requires an explicit disparate-impact audit. This is both a legal
and ethical blocker.

*Recommended action:* Before any deployment, run a fairness analysis (AUC by
ZIP-income quartile, by racial composition quartile). Document the analysis in
a companion Quarto notebook. Escalate to CEO if disparate impact is found.

### P1 — Required for soft-launch

**P1-A: No serving layer.**
There is no API, no Trigger.dev task, and no offline batch job that generates
scores. Predictions cannot reach any downstream system.

*Recommended action:* Once an artifact exists, build the simplest viable
serving path. For Uncle May's at current scale, this is likely a Trigger.dev
TypeScript task that:

1. Reads the latest `conversion_v2` parquet or calls a Python subprocess
2. Calls `predict_proba()` on the serialized model
3. Returns a JSON `{ attempt_id, score, threshold_flag }`

Alternatively: an R `plumber` API containerized in Docker on Cloud Run.
Discuss the trade-off with the Decision Scientist before choosing.

**P1-B: No ground-truth feedback loop.**
Predictions are only useful if we can later compare them to actual outcomes.
Without this loop, model monitoring is impossible.

*Recommended action:* Log every prediction (attempt_id, score, timestamp,
model_version) to a BigQuery table. The Stripe webhook already fires on
payment success/failure — join that signal back to the prediction log weekly.

**P1-C: GA4 attribution coverage below threshold.**
GA4 session features (pageviews, scroll depth, form starts, traffic source)
are the most valuable behavioral signals the model could use. As of 2026-05-02,
coverage was <1% (1 of 305 rows had a GA4 match). Attribution was fixed on
2026-05-03, but historic data cannot be backfilled. GA4 features will only
become reliable after several weeks of post-fix data accumulates.

*Recommended action:* Track GA4 join rate weekly as a data quality metric.
Do not use GA4 features as load-bearing in a production model until join rate
exceeds 30% (≈ 90 matched rows at 300-row scale, or ≈ 300 rows at 1,000-row
scale).

### P2 — Within 30 days of soft-launch

**P2-A: Hyperparameter tuning.**
Fixed hyperparameters are a research shortcut. Before committing to a model
architecture, run `tune_grid()` or `tune_bayes()` on the top-2 candidates.

**P2-B: Monitoring dashboard.**
Weekly: plot score distribution of new predictions vs. the training distribution.
Flag if KL-divergence exceeds a threshold. This can be a short Quarto document
auto-rendered by a Trigger.dev cron.

**P2-C: Retraining cadence.**
Define the trigger: "retrain weekly if new data adds >20 positives since last
retrain" OR "retrain on the 1st Sunday of each month." Document the owner
(ML Engineer) and the on-call escalation path.

**P2-D: Separate train/test split.**
Current evaluation is 5-fold CV only — no holdout. Once N ≥ 100 positives,
do a temporal holdout (most recent 20% of data by `created_at`) to get an
unbiased estimate of live performance.

---

## 4. Data Dependency Map

The `conversion_v2` feature pipeline requires the following raw parquet files,
all produced by `ml/ingest/*.py`:

```{r dep-map, results="asis"}
deps <- tribble(
  ~Source, ~Ingest_Script, ~Join_Key, ~Features_Added, ~Reliability,

  "Stripe Checkout Sessions", "ingest/stripe.py",
  "checkout_session_id", "Core attempt spine (label, amount, timestamps, UTMs)",
  "✅ Live",

  "Stripe Payment Intents", "ingest/stripe.py",
  "payment_intent_id", "Core attempt spine (label, amount, timestamps, UTMs, fbc/fbp/gclid)",
  "✅ Live",

  "Stripe Customers", "ingest/stripe.py",
  "customer_id", "Billing geo, delinquency flag",
  "✅ Live",

  "Stripe Charges", "ingest/stripe.py",
  "payment_intent_id", "Charge outcome columns (leakage-flagged — currently dropped in recipe)",
  "✅ Live",

  "Stripe Invoices / Subscriptions", "ingest/stripe.py",
  "—", "Not used in v2 model (subscription flow excluded from label)",
  "✅ Live",

  "GA4 Session Summary", "ingest/bigquery_ga4.py",
  "ga_client_id / payment_intent_id", "Device, browser, traffic source, pageviews, scrolls, form_starts",
  "⚠️ <1% join rate (pre-2026-05-03); improving post-fix",

  "Mailchimp Members", "ingest/mailchimp.py",
  "email_hash", "Subscription status, open/click rates, tag count",
  "✅ Live",

  "Resend Emails", "ingest/resend.py",
  "email_hash", "Send count, email type count",
  "✅ Live",

  "Apollo Contacts", "ingest/apollo.py",
  "email_hash", "Professional title, seniority, industry",
  "✅ Live",

  "Census ACS (ZIP)", "ingest/census.py",
  "shipping_zip", "Median income, population, age, household size, racial composition",
  "✅ Annual; refresh once/year",

  "Meta Campaign Insights", "ingest/meta_ads.py",
  "campaign_slug_canonical", "Lifetime impressions, clicks, spend, CTR, CPC per campaign",
  "✅ Live",

  "Google Ads Campaign Insights", "ingest/google_ads.py",
  "campaign_slug_canonical", "Lifetime impressions, clicks, spend, conversions, CTR, CPC",
  "✅ Live",

  "Checkout Store (local)", "ingest/checkout_store.py",
  "payment_intent_id", "Cart line count, total, fulfillment mode, recovery email flags",
  "⚠️ Partial — only post-2026-04-24 data",

  "Microsoft Clarity", "ingest/clarity.py",
  "—", "URL-level dwell/scroll/rage-click (NOT joined in v2 — noted as skipped)",
  "⚠️ Available but not used"
)

deps |>
  select(-Reliability) |>
  knitr::kable(caption = "Data dependencies for conversion_v2 feature pipeline")
```

### Reliability assessment

```{r reliability, results="asis"}
deps |>
  select(Source, Reliability) |>
  knitr::kable(caption = "Ingest reliability status (2026-05-03)")
```

**Key observations:**

1. **GA4 join rate is the critical gap.** All GA4 behavioral features are
   functionally null for the entire historical dataset. Post-fix data will
   accumulate from 2026-05-03 forward.

2. **Checkout Store is partial.** Only attempts from 2026-04-24 onward have
   cart-level features (line count, cart total, recovery flags). These may
   be among the most predictive features when sufficient history accumulates.

3. **No freshness SLA exists.** Ingest scripts are run manually. A broken
   ingest (e.g. Stripe rate limit, GA4 token expiry like the 48h gap on
   2026-04-29) can silently produce stale features. Recommend a daily
   freshness check: if any raw parquet is >36h old, alert the Data Engineer.

4. **Census ACS** is low-risk because it refreshes annually. Confirm the
   ACS vintage year and document it.

---

## 5. Recommended Next Steps (Prioritized)

| Priority | Owner | Action | Precondition |
|----------|-------|--------|-------------|
| P0-A | Data Engineer + DE Scientist | Monitor weekly: track cumulative positives in Stripe; surface when N_pos > 50, 100 | — |
| P0-C | Decision Scientist | Fairness audit on Census ACS demographic features | Can run now on current data |
| P0-B | ML Engineer | Add `saveRDS()` / `joblib.dump()` to training notebook | N_pos ≥ 100 |
| P1-B | ML Engineer | Create BQ prediction log table; log every future score | Serving layer |
| P1-A | ML Engineer | Build minimal serving layer (Trigger.dev task or R plumber) | Model artifact |
| P1-C | Data Engineer | Track and report GA4 join rate weekly | Attribution fix live |
| P2-A | Decision Scientist | Hyperparameter tuning (tune_grid / tune_bayes) | N_pos ≥ 100 |
| P2-B | ML Engineer | Weekly score-distribution monitoring Quarto | Prediction log |
| P2-D | Decision Scientist | Temporal train/test split evaluation | N_pos ≥ 100 |

---

## 6. Reviewer Sign-Off

This document is submitted for review under [UNC-768](/UNC/issues/UNC-768).
Required reviewers:

- [ ] **Decision Scientist** — validate model summary accuracy and gap prioritization
- [ ] **CEO (Anthony Ivy)** — acknowledge readiness verdict before any production deployment decision

No model deployment actions will be taken until both reviewers sign off.

---

*Generated by ML Engineer agent (c57979b2) · Run 32bb7114 · 2026-05-03*
