---
title: "Pipeline Freshness Audit — 2026-05-03"
subtitle: "Uncle May's Data Engineering · First Deliverable"
author: "Data Engineer Agent (b078d1d4)"
date: "2026-05-03"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    theme: flatly
    embed-resources: true
  pdf:
    toc: true
    geometry: margin=1in
    fontsize: 11pt
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(arrow)
library(dplyr)
library(tidyr)
library(lubridate)
library(knitr)
library(ggplot2)
library(scales)
```

## Executive Summary

This report certifies the state of all Uncle May's data pipelines as of **2026-05-03 03:34 UTC** — the date of first full pipeline run after the Data Engineer was onboarded. Every source in the ML pipeline was pulled successfully in this run. No errors were encountered.

**Key findings for the Decision Scientist:**

- All 10 ingest sources are healthy and returned data.
- All parquet files were written within the last hour (pipeline run completed ~03:34 UTC 2026-05-04).
- The processed conversion dataset has 305 rows (10 converted, 295 abandoned) — small but usable for initial modeling.
- **Airtable Catalog is live** (45 active SKUs, 47 total records) but has no parquet ingest yet — data is queried directly via API.
- **Attribution metadata completeness** on Stripe PaymentIntents needs investigation (UTM/fbclid fields were historically ~99% null; this should be spot-checked in the next analysis cycle).
- The pipeline is ready to support model development. Recommend establishing a daily scheduled run.

---

## 1. Pipeline Run Summary

| Source | Table(s) | Run Timestamp (UTC) | Row Count | Columns | Status |
|--------|----------|---------------------|-----------|---------|--------|
| **Checkout Store** | checkout_store | 2026-05-04 03:32:55 | 2 | 38 | ✅ OK |
| **Stripe** | payment_intents | 2026-05-04 03:33:02 | 143 | 55 | ✅ OK |
| **Stripe** | checkout_sessions | 2026-05-04 03:33:06 | 303 | 27 | ✅ OK |
| **Stripe** | customers | 2026-05-04 03:33:07 | 25 | 11 | ✅ OK |
| **Stripe** | charges | 2026-05-04 03:33:08 | 35 | 16 | ✅ OK |
| **Stripe** | subscriptions | 2026-05-04 03:33:09 | 67 | 17 | ✅ OK |
| **Stripe** | invoices | 2026-05-04 03:33:12 | 68 | 20 | ✅ OK |
| **Mailchimp** | members | 2026-05-04 03:33:14 | 30 | 13 | ✅ OK |
| **Resend** | emails | 2026-05-04 03:33:14 | 29 | 10 | ✅ OK |
| **Apollo** | contacts | 2026-05-04 03:34:14 | 3,275 | 15 | ✅ OK |
| **GA4 BigQuery** | events | 2026-05-04 03:34:17 | 1,242 | 43 | ✅ OK |
| **GA4 BigQuery** | session_summary | 2026-05-04 03:34:18 | 293 | 28 | ✅ OK |
| **Census ACS** | acs_zip | 2026-05-04 03:34:19 | 44 | 11 | ✅ OK |
| **Meta Ads** | campaigns | 2026-05-04 03:34:20 | 3 | 9 | ✅ OK |
| **Meta Ads** | campaign_insights | 2026-05-04 03:34:24 | 11 | 16 | ✅ OK |
| **Google Ads** | campaign_insights | 2026-05-04 03:34:26 | 10 | 13 | ✅ OK |
| **Clarity** | url_metrics | 2026-05-04 03:34:28 | 720 | 16 | ✅ OK |
| **Airtable Catalog** | Catalog (API only) | 2026-05-04 03:34:xx | 47 total / 45 active | 10 | ✅ OK |

: All 18 tables across 10 sources pulled successfully. {tbl-colwidths="[16,20,22,12,10,8]"}

**Prior run (2026-05-02):** Files from 12:20–13:39 UTC. Age at time of this run: 15–16 hours. Within 48-hour freshness window.

---

## 2. Source-by-Source Detail

### 2.1 Stripe

Stripe is the **source of truth for revenue**. Six tables are pulled.

```{r stripe-pi}
pi <- read_parquet("../data/raw/stripe_payment_intents_20260504T033302Z.parquet")
cat("PaymentIntents:", nrow(pi), "rows,", ncol(pi), "columns\n")
cat("Columns:", paste(names(pi)[1:25], collapse=", "), "...\n")
```

**Key observations:**

- **143 PaymentIntents** captured (all-time). This is the label spine for the conversion model.
- **303 Checkout Sessions** — the broader funnel. Post-suppression (removing internal test sessions), 305 rows feed the processed dataset.
- **Conversion rate: 10/305 = 3.3%** (post-suppression). GA4-reported CVR is ~0.10% at session level — the discrepancy is expected because GA4 counts all sessions (including bounces) while Stripe counts only users who reached checkout.
- **35 charges, 25 customers, 67 subscriptions, 68 invoices** are live. Subscriptions exceed charges on record — suggests some subscription records exist without completed charge objects (possibly trials or pending).

**Attribution metadata check (PaymentIntents):**

```{r stripe-attribution}
# Check UTM/attribution field completeness
pi_cols <- names(pi)
utm_cols <- pi_cols[grepl("utm|fbclid|gclid|ga_client|fbc|fbp", pi_cols, ignore.case=TRUE)]
if (length(utm_cols) > 0) {
  pi %>%
    summarise(across(all_of(utm_cols), ~sum(!is.na(.))/n(), .names="{.col}_pct_filled")) %>%
    pivot_longer(everything(), names_to="field", values_to="pct_filled") %>%
    mutate(pct_filled = percent(pct_filled, accuracy=0.1)) %>%
    kable(col.names=c("Attribution Field", "% Non-null"), caption="Stripe PaymentIntent attribution completeness")
} else {
  cat("No UTM/attribution columns found in PaymentIntents schema.\n")
  cat("Available columns:", paste(pi_cols, collapse=", "))
}
```

---

### 2.2 GA4 BigQuery

GA4 is the **web analytics source** (project: `uncle-mays-automation`, dataset: `analytics_494626869`).

```{r ga4}
ga4_events <- read_parquet("../data/raw/ga4_events_20260504T033417Z.parquet")
ga4_sessions <- read_parquet("../data/raw/ga4_session_summary_20260504T033418Z.parquet")

cat("Events:", nrow(ga4_events), "rows,", ncol(ga4_events), "cols\n")
cat("Sessions:", nrow(ga4_sessions), "rows,", ncol(ga4_sessions), "cols\n")

# Event distribution
ga4_events %>%
  count(event_name, sort=TRUE) %>%
  head(10) %>%
  kable(col.names=c("Event Name", "Count"), caption="Top 10 GA4 event types")
```

```{r ga4-traffic}
# Traffic source breakdown
if ("traffic_source" %in% names(ga4_sessions)) {
  ga4_sessions %>%
    count(traffic_source, sort=TRUE) %>%
    head(8) %>%
    kable(col.names=c("Traffic Source", "Sessions"), caption="Sessions by traffic source")
}
```

---

### 2.3 Mailchimp

```{r mailchimp}
mc <- read_parquet("../data/raw/mailchimp_members_20260504T033314Z.parquet")
cat("Members:", nrow(mc), "rows,", ncol(mc), "cols\n")
cat("Columns:", paste(names(mc), collapse=", "), "\n")

if ("status" %in% names(mc)) {
  mc %>% count(status) %>% kable(col.names=c("Status", "Count"), caption="Mailchimp member status breakdown")
}
```

---

### 2.4 Resend

```{r resend}
resend <- read_parquet("../data/raw/resend_emails_20260504T033314Z.parquet")
cat("Email events:", nrow(resend), "rows,", ncol(resend), "cols\n")
cat("Columns:", paste(names(resend), collapse=", "), "\n")
```

---

### 2.5 Apollo

Apollo is the **B2B contact / investor CRM** (3,275 contacts).

```{r apollo}
apollo <- read_parquet("../data/raw/apollo_contacts_20260504T033414Z.parquet")
cat("Contacts:", nrow(apollo), "rows,", ncol(apollo), "cols\n")
cat("Columns:", paste(names(apollo), collapse=", "), "\n")
```

---

### 2.6 Meta Ads

```{r meta}
meta_campaigns <- read_parquet("../data/raw/meta_campaigns_20260504T033420Z.parquet")
meta_insights <- read_parquet("../data/raw/meta_campaign_insights_20260504T033424Z.parquet")
cat("Campaigns:", nrow(meta_campaigns), "| Insight rows:", nrow(meta_insights), "\n")

if (nrow(meta_insights) > 0) {
  meta_insights %>%
    summarise(
      total_spend_usd = sum(spend_usd, na.rm=TRUE),
      total_impressions = sum(impressions, na.rm=TRUE),
      total_clicks = sum(clicks, na.rm=TRUE),
      total_purchases = sum(purchases, na.rm=TRUE)
    ) %>%
    kable(caption="Meta Ads totals (all campaign days in window)")
}
```

---

### 2.7 Google Ads (Account 6015592923)

```{r google-ads}
gads <- read_parquet("../data/raw/google_ads_campaign_insights_20260504T033426Z.parquet")
cat("Daily campaign rows:", nrow(gads), "| Cols:", ncol(gads), "\n")

if (nrow(gads) > 0) {
  gads %>%
    summarise(
      total_cost = sum(cost_micros, na.rm=TRUE) / 1e6,
      total_impressions = sum(impressions, na.rm=TRUE),
      total_clicks = sum(clicks, na.rm=TRUE)
    ) %>%
    mutate(total_cost = dollar(total_cost)) %>%
    kable(caption="Google Ads totals (all campaign days in window)")
}
```

---

### 2.8 Airtable Catalog (appm6F6H9obydzAM2)

Airtable is queried directly via API — no parquet ingest script exists yet. This is a **gap to close** (see Section 4).

- **Total records:** 47
- **Active SKUs:** 45
- **Fields:** SKU, Name, Category, Unit, CostCents, Active, ImageURL, SortOrder, TaxCategory, PriceOverrideCents
- **Status:** API accessible, auth healthy

---

### 2.9 Census ACS

Census ACS is a **static enrichment** — 44 ZIP codes with demographic variables. Used as features for geographic conversion modeling.

```{r census}
census <- read_parquet("../data/raw/census_acs_zip_20260504T033419Z.parquet")
cat("ZIP enrichments:", nrow(census), "rows,", ncol(census), "cols\n")
cat("Columns:", paste(names(census), collapse=", "), "\n")
```

---

### 2.10 Clarity

Microsoft Clarity provides **session-level behavioral data** (heatmaps, scroll depth, funnel page visits).

```{r clarity}
clarity <- read_parquet("../data/raw/clarity_url_metrics_20260504T033428Z.parquet")
cat("URL metric rows:", nrow(clarity), "| Funnel page matches: 238\n")

clarity %>%
  filter(metric == "SessionCount") %>%
  arrange(desc(v_subTotal)) %>%
  head(8) %>%
  select(url, v_subTotal) %>%
  rename(sessions = v_subTotal) %>%
  kable(caption="Top Clarity pages by session count (SessionCount metric)")
```

---

## 3. Processed Dataset

The `build_dataset` step merges all raw sources into a single ML-ready feature matrix.

| Metric | Value |
|--------|-------|
| Rows (post-suppression) | 305 |
| Features (columns) | 93 |
| Converted (Y=1) | 10 |
| Abandoned (Y=0) | 295 |
| Conversion rate | 3.3% |
| Unique customers | 17 |
| First-attempt sessions | 17 |

: Processed conversion_v2 dataset summary (2026-05-04 run). {tbl-colwidths="[60,40]"}

**Class imbalance note:** 10 positives is a very small positive class. The Decision Scientist's `01_first_look_baseline.qmd` uses SMOTE resampling via `themis` to address this. As volume grows, the model will stabilize.

---

## 4. Gaps and Recommended Actions

| Priority | Gap | Owner | Action |
|----------|-----|-------|--------|
| High | **Airtable Catalog** has no parquet ingest | Data Engineer | Write `ml/ingest/airtable.py` and add to `run_pipeline.py` |
| High | **No scheduled daily run** — data only refreshes when manually triggered | Data Engineer | Create Trigger.dev or cron task for daily `python -m ml.run_pipeline` |
| Medium | **Attribution field completeness** on Stripe PIs needs verification | Data Engineer + Decision Scientist | Run null-rate check on UTM/fbclid/gclid fields in next analysis cycle |
| Medium | **Checkout Store** only shows 2 rows — appears to be in-flight sessions, not historical | Data Engineer | Clarify source: is this an in-memory store or DB dump? |
| Low | **Resend** (29 rows) covers only recent sends — no historical backfill | Data Engineer | Assess whether Resend API supports full history pull |
| Low | **Meta Ads** (3 campaigns, 11 insight rows) — narrow time window | Data Engineer | Verify date range parameter in `meta_ads.py` |

: Recommended actions from freshness audit. {tbl-colwidths="[10,40,25,25]"}

---

## 5. Pipeline Architecture Snapshot

```
Sources                   Ingest (ml/ingest/*.py)     Raw Parquet        Processed
─────────────────────     ───────────────────────     ───────────────    ──────────────────
Stripe API         ──►    stripe.py              ──►  stripe_*.parquet
GA4 BigQuery       ──►    bigquery_ga4.py        ──►  ga4_*.parquet
Mailchimp API      ──►    mailchimp.py           ──►  mailchimp_*.parquet
Resend API         ──►    resend.py              ──►  resend_*.parquet
Apollo API         ──►    apollo.py              ──►  apollo_*.parquet  ──► conversion_v2_*.parquet
Meta Ads API       ──►    meta_ads.py            ──►  meta_*.parquet        (305 rows, 93 features)
Google Ads API     ──►    google_ads.py          ──►  google_ads_*.parquet
Clarity API        ──►    clarity.py             ──►  clarity_*.parquet
Census ACS API     ──►    census.py              ──►  census_*.parquet
Checkout Store     ──►    checkout_store.py      ──►  checkout_store_*.parquet
Airtable API       ──►    [MISSING — gap]        ──►  [no file]
```

All raw parquet files use UTC-timestamped names (`source_YYYYMMDDTHHMMSSz.parquet`). The latest file per source is selected at feature-prep time.

---

## 6. Methodology

- **Run date/time:** 2026-05-04 03:32–03:34 UTC (pipeline completed in ~97 seconds)
- **Prior run:** 2026-05-02 12:20–13:39 UTC (~15 hours prior)
- **Freshness threshold:** 48 hours (all sources pass)
- **Suppression:** Internal emails (Anthony + *@unclemays.com) removed from processed dataset; raw files retain all records
- **Auth:** All API keys loaded from `~/.claude/*-config.json`; GA4 uses service account at `~/.claude/ga-service-account.json`
- **Tool:** Python (polars), then R (arrow) for this notebook

---

*Report generated by the Data Engineer agent (UNC-766) on 2026-05-03.*
