---
title: "Uncle May's Metrics Glossary"
subtitle: "Single source of truth for every metric quoted in a board deck"
author: "Analytics Engineer"
date: "2026-05-03"
date-modified: today
format:
  html:
    toc: true
    toc-depth: 3
    theme: flatly
    code-fold: true
    self-contained: true
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    geometry: margin=1in
    fontsize: 11pt
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
#| include: false
library(arrow)
library(dplyr)
library(lubridate)
library(scales)
library(knitr)
library(kableExtra)

# Load raw parquet data — path relative to notebooks/ directory
raw_dir <- normalizePath("../data/raw", mustWork = FALSE)

# Helper: get latest file matching a glob pattern
latest_parquet <- function(pattern) {
  files <- list.files(raw_dir, pattern = pattern, full.names = TRUE)
  if (length(files) == 0) return(NULL)
  files[which.max(file.mtime(files))]
}

pi_path  <- latest_parquet("stripe_payment_intents")
cs_path  <- latest_parquet("stripe_checkout_sessions")
chg_path <- latest_parquet("stripe_charges")
cust_path <- latest_parquet("stripe_customers")

pi   <- if (!is.null(pi_path))   read_parquet(pi_path)   else tibble()
cs   <- if (!is.null(cs_path))   read_parquet(cs_path)   else tibble()
chg  <- if (!is.null(chg_path))  read_parquet(chg_path)  else tibble()
cust <- if (!is.null(cust_path)) read_parquet(cust_path) else tibble()

# Orders = succeeded, non-test payment intents
orders <- pi |>
  filter(status == "succeeded", !isTRUE(is_test)) |>
  mutate(
    amount_dollars = amount_received_cents / 100,
    order_week  = floor_date(as.Date(created_at), "week", week_start = 1),
    order_month = floor_date(as.Date(created_at), "month")
  )

ingest_date <- "2026-05-02"
```

::: {.callout-note}
**Data freshness:** Metrics in this document are computed from raw Stripe parquet
files ingested on **`r ingest_date`**. Re-run `ml/ingest/stripe.py` and
re-render this document to refresh all numbers.
:::

# Purpose & Governance

This document is the **single source of truth** for every metric Uncle May's uses
in board decks, marketing reports, and operational reviews. If a number in any
report disagrees with a number computed from the SQL in this glossary, the SQL
wins.

**Owner:** Analytics Engineer (`analytics-engineer` on Paperclip).
**Review cadence:** Quarterly or whenever a new metric is added to a board deck.
**Source of record:** `ml/notebooks/metrics-glossary.qmd` committed to the
website repository.
**dbt models:** `ml/dbt/uncle_mays/` (see README.md for run instructions).

---

# Revenue Metrics

## Average Order Value (AOV)

**Definition:** Mean gross revenue per completed order, in USD.

**Formula:** `sum(amount_received_cents) / count(orders) / 100`

**Source table:** `mart_orders` (dbt) → `stg_stripe_payment_intents` → raw parquet

**Scope:** Orders with `status = 'succeeded'` and `is_test = false`.

**SQL:**
```sql
select avg(gross_revenue_dollars) as aov_dollars
from mart_orders
```

**Current value (as of `r ingest_date`):**

```{r aov}
aov_val <- mean(orders$amount_dollars)
n_orders <- nrow(orders)
tibble(
  Metric = "AOV",
  Value = dollar(aov_val),
  `N Orders` = n_orders
) |>
  kable(align = c("l","r","r")) |>
  kable_styling(bootstrap_options = c("condensed"), full_width = FALSE)
```

**Notes:** AOV is computed on gross revenue (amount actually received by Stripe).
Refunded amounts should be subtracted when computing net AOV; refund tracking
is not yet wired into the mart.

---

## Weekly Revenue

**Definition:** Sum of gross revenue for all completed orders in a calendar week
(Monday–Sunday ISO week).

**Formula:** `sum(gross_revenue_dollars) group by order_week`

**Source table:** `mart_orders`

**SQL:**
```sql
select
  order_week,
  sum(gross_revenue_dollars) as weekly_revenue_dollars,
  count(*)                   as weekly_orders
from mart_orders
group by order_week
order by order_week
```

**Current values:**

```{r weekly_revenue}
weekly <- orders |>
  group_by(order_week) |>
  summarise(
    orders  = n(),
    revenue = sum(amount_dollars),
    .groups = "drop"
  ) |>
  mutate(
    revenue_fmt  = dollar(revenue),
    week_label   = format(order_week, "%b %d, %Y")
  )

weekly |>
  select(`Week of` = week_label, Orders = orders, Revenue = revenue_fmt) |>
  kable(align = c("l", "r", "r")) |>
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE)
```

**Goal:** 30 orders/week (`d45fd7bc` on Paperclip). Current peak:
`r max(weekly$orders)` orders (week of
`r format(weekly$order_week[which.max(weekly$orders)], "%b %d, %Y")`).

---

## Gross Revenue (All-Time)

**Definition:** Cumulative sum of `amount_received_cents` across all succeeded,
non-test payment intents.

```{r total_revenue}
tibble(
  Metric = "All-time gross revenue",
  Value  = dollar(sum(orders$amount_dollars))
) |>
  kable(align = c("l","r")) |>
  kable_styling(bootstrap_options = c("condensed"), full_width = FALSE)
```

---

# Customer Metrics

## Customer Lifetime Value (LTV)

**Definition:** Total gross revenue attributed to a single customer across all
their orders, identified by email address.

**Formula:** `sum(gross_revenue_dollars) group by email_hash`

**Source table:** `mart_customers` (dbt)

**SQL:**
```sql
select
  email_hash,
  ltv_dollars,
  total_orders
from mart_customers
order by ltv_dollars desc
```

**Distribution (current):**

```{r ltv}
ltv <- orders |>
  group_by(email) |>
  summarise(
    ltv    = sum(amount_dollars),
    orders = n(),
    .groups = "drop"
  )

tibble(
  Statistic  = c("N customers", "Min LTV", "Median LTV", "Mean LTV", "Max LTV"),
  Value      = c(
    as.character(nrow(ltv)),
    dollar(min(ltv$ltv)),
    dollar(median(ltv$ltv)),
    dollar(mean(ltv$ltv)),
    dollar(max(ltv$ltv))
  )
) |>
  kable(align = c("l","r")) |>
  kable_styling(bootstrap_options = c("condensed"), full_width = FALSE)
```

::: {.callout-warning}
**Small sample caveat:** Only `r nrow(ltv)` unique customers in the current
dataset. LTV statistics are not stable at this scale. Revisit after N ≥ 50.
:::

---

## Repeat Purchase Rate

**Definition:** Fraction of customers who have placed more than one order.

**Formula:** `count(customers where total_orders > 1) / count(all customers)`

**Source table:** `mart_customers`

**SQL:**
```sql
select
  countif(total_orders > 1) / count(*) as repeat_rate,
  countif(total_orders > 1)            as repeat_customers,
  count(*)                             as total_customers
from mart_customers
```

**Current value:**

```{r repeat_rate}
n_repeat <- sum(ltv$orders > 1)
n_total  <- nrow(ltv)
tibble(
  Metric = c("Total customers", "Repeat customers", "Repeat rate"),
  Value  = c(
    as.character(n_total),
    as.character(n_repeat),
    percent(n_repeat / n_total, accuracy = 0.1)
  )
) |>
  kable(align = c("l","r")) |>
  kable_styling(bootstrap_options = c("condensed"), full_width = FALSE)
```

::: {.callout-warning}
**Interpretation caution:** The current repeat rate is driven by 2 customers
with 18 and 9 orders respectively. This is not a stable cohort-based retention
metric. Once the customer base grows, compute retention properly as
"fraction of month-1 customers who placed an order in month-2+."
:::

---

## Customer Acquisition

**Definition:** Number of new unique customers acquired in a given period
(first-ever order in that period).

**Source table:** `mart_customers` (acquisition_month column)

**SQL:**
```sql
select
  acquisition_month,
  count(*) as new_customers
from mart_customers
group by acquisition_month
order by acquisition_month
```

---

# Conversion Metrics

## Checkout Conversion Rate

**Definition:** Fraction of Stripe Checkout Sessions where payment was collected
(`payment_status = 'paid'`).

**Formula:** `count(payment_status = 'paid') / count(*)`

**Source table:** `stg_stripe_checkout_sessions`

**SQL:**
```sql
select
  count(case when is_converted then 1 end)  as converted_sessions,
  count(*)                                  as total_sessions,
  avg(cast(is_converted as int)) * 100      as checkout_cvr_pct
from stg_stripe_checkout_sessions
```

**Current value:**

```{r checkout_cvr}
if (nrow(cs) > 0) {
  paid  <- sum(cs$payment_status == "paid", na.rm = TRUE)
  total <- nrow(cs)
  tibble(
    Metric = c("Total sessions", "Paid sessions", "Checkout CVR"),
    Value  = c(
      comma(total),
      comma(paid),
      percent(paid/total, accuracy = 0.1)
    )
  ) |>
    kable(align = c("l","r")) |>
    kable_styling(bootstrap_options = c("condensed"), full_width = FALSE)
}
```

**Notes:**
- Sessions prior to 2026-05-03 lack UTM/attribution metadata.
- Checkout CVR ≠ site-wide conversion rate. Site-wide CVR uses GA4 sessions
  as the denominator (see section below).

---

## Site-Wide Conversion Rate (GA4)

**Definition:** Fraction of GA4 sessions that resulted in a completed purchase.

**Formula:** `purchase_events / total_sessions` from GA4 BigQuery export.

**Source:** `analytics_494626869.events_YYYYMMDD` (BigQuery, daily sharded)

**SQL (BigQuery):**
```sql
select
  count(distinct session_id)                                          as sessions,
  count(distinct case when event_name = 'purchase' then session_id end)
                                                                      as purchase_sessions,
  safe_divide(
    count(distinct case when event_name = 'purchase' then session_id end),
    count(distinct session_id)
  )                                                                   as site_cvr
from `uncle-mays-automation.analytics_494626869.events_*`
where _table_suffix between '20260429' and format_date('%Y%m%d', current_date())
```

**Baseline:** 0.10% site-wide CVR as of CIO audit 2026-04-29.
GA4 export only started 2026-04-29; historical data is not available.

---

## Checkout Abandonment Rate

**Definition:** Fraction of checkout sessions where the customer did not pay
and the session expired.

**Formula:** `1 - checkout_cvr`

```{r abandonment}
if (nrow(cs) > 0) {
  paid  <- sum(cs$payment_status == "paid", na.rm = TRUE)
  total <- nrow(cs)
  tibble(
    Metric = "Abandonment rate",
    Value  = percent(1 - paid/total, accuracy = 0.1)
  ) |>
    kable(align = c("l","r")) |>
    kable_styling(bootstrap_options = c("condensed"), full_width = FALSE)
}
```

---

# Marketing & Acquisition Metrics

## Customer Acquisition Cost (CAC)

**Definition:** Total paid ad spend divided by number of new customers acquired
in the same period, by channel.

**Formula:** `sum(ad_spend_dollars) / count(new_customers)` by channel/week

**Source table:** `mart_channel_performance` (dbt)

**SQL:**
```sql
select
  order_week,
  channel,
  ad_spend_dollars,
  new_customers,
  ad_spend_dollars / nullif(new_customers, 0) as cac_dollars
from mart_channel_performance
```

**Status:** ⚠️ **Not computable.** Meta Ads and Google Ads parquet data
exists at `ml/data/raw/` but has not been loaded to BigQuery yet.
CAC will be available once:
1. `ml/ingest/meta_ads.py` and `ml/ingest/google_ads.py` outputs are
   loaded to BQ (`meta_ads_raw` and `google_ads_raw` datasets), and
2. `mart_ad_spend` dbt model is built.

---

## Return on Ad Spend (ROAS)

**Definition:** Gross revenue divided by ad spend in the same period and channel.

**Formula:** `sum(gross_revenue_dollars) / sum(ad_spend_dollars)`

**Status:** ⚠️ **Not computable.** Same blocker as CAC above.

---

# Financial Metrics

## Gross Margin

**Definition:** (Gross Revenue − COGS) / Gross Revenue.

**Status:** ⚠️ **Not computable.** COGS requires:
1. SKU-level cost data from the COO (vendor prices, not yet in Airtable)
2. SKU quantities per order (requires parsing `cart_json` in `mart_orders`)

Once cost data is available, this will be built as `mart_sku_margin`.

---

## Contribution Margin per SKU

**Definition:** (Revenue per unit − Variable cost per unit) / Revenue per unit.

**Status:** ⚠️ **Not computable.** Same blocker as gross margin.
Customer-facing prices are in Airtable (`appm6F6H9obydzAM2` table `Catalog`).
Vendor costs are not yet tracked.

---

# Data Quality Notes

| Source | Freshness | Known Issues |
|--------|-----------|--------------|
| Stripe PaymentIntents | 2026-05-02 | UTM/fbclid/gclid null before 2026-05-03 (attribution fix date) |
| Stripe CheckoutSessions | 2026-05-02 | 285 of 303 sessions unpaid; includes visitors who opened but never submitted checkout |
| Stripe Charges | 2026-05-02 | Matches PIs closely but 15 fewer rows; some PIs have no charge record |
| GA4 BigQuery export | Daily from 2026-04-29 | Short history; no pre-2026-04-29 session data |
| Meta Ads | 2026-05-02 | Parquet exists locally; not in BQ yet |
| Google Ads | 2026-05-02 | Parquet exists locally; not in BQ yet |
| Mailchimp | 2026-05-02 | Members parquet available; not yet joined to orders |
| Airtable Catalog | Live | 45 active SKUs; no vendor cost column |

---

# Appendix: Metric Ownership

| Metric | dbt Model | Status | Owner | Last Reviewed |
|--------|-----------|--------|-------|---------------|
| AOV | mart_orders | Live | Analytics Engineer | 2026-05-03 |
| Weekly Revenue | mart_orders | Live | Analytics Engineer | 2026-05-03 |
| All-time Revenue | mart_orders | Live | Analytics Engineer | 2026-05-03 |
| Customer LTV | mart_customers | Live | Analytics Engineer | 2026-05-03 |
| Repeat Purchase Rate | mart_customers | Live | Analytics Engineer | 2026-05-03 |
| Checkout CVR | stg_stripe_checkout_sessions | Live | Analytics Engineer | 2026-05-03 |
| Site-wide CVR | GA4 (BQ direct) | Live (BQ only) | Analytics Engineer | 2026-05-03 |
| CAC | mart_channel_performance | Pending ad spend load | Analytics Engineer | — |
| ROAS | mart_channel_performance | Pending ad spend load | Analytics Engineer | — |
| Gross Margin | mart_sku_margin (not built) | Pending COGS data | Analytics Engineer | — |
| Contribution Margin/SKU | mart_sku_margin (not built) | Pending COGS data | Analytics Engineer | — |
