---
title: "Uncle May's Metrics Glossary"
subtitle: "Single source of truth for every metric quoted in a board deck"
author: "Analytics Engineer"
date: "2026-05-03"
date-modified: today
format:
  html:
    toc: true
    toc-depth: 3
    theme: flatly
    code-fold: true
    self-contained: true
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    geometry: margin=1in
    fontsize: 11pt
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
#| include: false
library(arrow)
library(dplyr)
library(lubridate)
library(scales)
library(knitr)
library(kableExtra)
library(tidyr)

# Load raw parquet data — path relative to notebooks/ directory
raw_dir <- normalizePath("../data/raw", mustWork = FALSE)

# Helper: get latest file matching a glob pattern
latest_parquet <- function(pattern) {
  files <- list.files(raw_dir, pattern = pattern, full.names = TRUE)
  if (length(files) == 0) return(NULL)
  files[which.max(file.mtime(files))]
}

pi_path   <- latest_parquet("stripe_payment_intents")
cs_path   <- latest_parquet("stripe_checkout_sessions")
chg_path  <- latest_parquet("stripe_charges")
cust_path <- latest_parquet("stripe_customers")
ga4_path  <- latest_parquet("ga4_session_summary")
meta_path <- latest_parquet("meta_campaign_insights")
gads_path <- latest_parquet("google_ads_campaign_insights")

pi   <- if (!is.null(pi_path))   read_parquet(pi_path)   else tibble()
cs   <- if (!is.null(cs_path))   read_parquet(cs_path)   else tibble()
chg  <- if (!is.null(chg_path))  read_parquet(chg_path)  else tibble()
cust <- if (!is.null(cust_path)) read_parquet(cust_path) else tibble()
ga4  <- if (!is.null(ga4_path))  read_parquet(ga4_path)  else tibble()
meta <- if (!is.null(meta_path)) read_parquet(meta_path) else tibble()
gads <- if (!is.null(gads_path)) read_parquet(gads_path) else tibble()

# Orders = succeeded, non-test payment intents
orders <- pi |>
  filter(status == "succeeded", !isTRUE(is_test)) |>
  mutate(
    amount_dollars = amount_received_cents / 100,
    created_at_dt  = as_datetime(created_at),
    order_date     = as.Date(created_at_dt),
    order_week     = floor_date(order_date, "week", week_start = 1),
    order_month    = floor_date(order_date, "month")
  )

ref_date   <- as.Date("2026-05-03")
ingest_date <- "2026-05-02"

# Customer-level aggregation
customers <- orders |>
  group_by(email) |>
  summarise(
    first_order   = min(order_date),
    last_order    = max(order_date),
    total_orders  = n(),
    ltv_dollars   = sum(amount_dollars),
    .groups = "drop"
  )
```

::: {.callout-note}
**Data freshness:** Metrics in this document are computed from raw Stripe parquet
files ingested on **`r ingest_date`**. Re-run `ml/ingest/stripe.py` and
re-render this document to refresh all numbers.
:::

# Purpose & Governance

This document is the **single source of truth** for every metric Uncle May's uses
in board decks, marketing reports, and operational reviews. If a number in any
report disagrees with a number computed from the definitions in this glossary,
the glossary wins.

**Owner:** Analytics Engineer (`analytics-engineer` on Paperclip).
**Review cadence:** Quarterly or whenever a new metric is added to a board deck.
**Source of record:** `ml/notebooks/metrics-glossary.qmd` committed to the
website repository.
**Goal this glossary serves:** 30 orders/week from the online produce box
(Paperclip goal `d45fd7bc`).

---

# Revenue Metrics

## Average Order Value (AOV)

**Business definition:** The mean amount a customer spends per order. Informs
pricing strategy, free-shipping thresholds, and upsell opportunity. If AOV
rises we need fewer orders to hit weekly revenue targets.

**Formula:** `sum(gross_revenue_dollars) / count(orders)`

**Time window:** Rolling or as-of-period; always specify the window when cited.

**Source table:** `mart_orders` (dbt) → `stg_stripe_payment_intents` → raw parquet

**Scope:** `status = 'succeeded'` AND `is_test = false`.

**SQL:**
```sql
select
  avg(gross_revenue_dollars) as aov_dollars
from mart_orders
```

**Current data availability:** ✅ Computable today from Stripe parquet.

**Target:** $65–$95 (aligns with the current box tier pricing: $35, $65, $95 boxes;
goal is upselling customers toward the upper tiers). At 30 orders/week with AOV
of $65, weekly revenue = $1,950.

**Current value (as of `r ingest_date`):**

```{r aov}
aov_val  <- mean(orders$amount_dollars)
n_orders <- nrow(orders)
tibble(
  Metric   = "AOV",
  Value    = dollar(aov_val),
  `N Orders` = n_orders
) |>
  kable(align = c("l","r","r")) |>
  kable_styling(bootstrap_options = c("condensed"), full_width = FALSE)
```

**AOV by SKU category:**

::: {.callout-warning}
**Data gap:** `cart_json` is only populated for a subset of orders (attribution
wiring was incomplete before 2026-05-03). AOV by SKU category is not computable
until cart-level data is consistently captured. Track via [UNC-767](/UNC/issues/UNC-767).
:::

---

## Weekly Revenue

**Business definition:** Gross revenue for all completed orders in a calendar week
(Monday–Sunday ISO). The primary operational heartbeat metric: are we trending
toward the 30-orders/week goal?

**Formula:** `sum(gross_revenue_dollars) GROUP BY order_week`

**Source table:** `mart_orders`

**SQL:**
```sql
select
  order_week,
  sum(gross_revenue_dollars) as weekly_revenue_dollars,
  count(*)                   as weekly_orders
from mart_orders
group by order_week
order by order_week
```

**Current data availability:** ✅ Computable today.

**Target:** 30 orders/week → ~$1,950/week at $65 AOV.

**Current values:**

```{r weekly_revenue}
weekly <- orders |>
  group_by(order_week) |>
  summarise(
    orders  = n(),
    revenue = sum(amount_dollars),
    .groups = "drop"
  ) |>
  mutate(
    revenue_fmt = dollar(revenue),
    week_label  = format(order_week, "%b %d, %Y")
  )

weekly |>
  select(`Week of` = week_label, Orders = orders, Revenue = revenue_fmt) |>
  kable(align = c("l","r","r")) |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)
```

**Goal:** 30 orders/week. Current peak: **`r max(weekly$orders)` orders**
(week of `r format(weekly$order_week[which.max(weekly$orders)], "%b %d, %Y")`).

---

## Gross Revenue (All-Time)

**Business definition:** Cumulative received revenue since launch.

```{r total_revenue}
tibble(
  Metric = "All-time gross revenue",
  Value  = dollar(sum(orders$amount_dollars))
) |>
  kable(align = c("l","r")) |>
  kable_styling(bootstrap_options = c("condensed"), full_width = FALSE)
```

---

# Customer Metrics

## Customer Lifetime Value (LTV)

**Business definition:** Total gross revenue from a single customer across all their
orders. Informs how much we can afford to spend to acquire a customer (see CAC),
and which customer segments are most valuable to retain.

**Formula:** `sum(gross_revenue_dollars) GROUP BY email`

**Time-windowed variants:** LTV is always computed from first order to the
measurement date. For board reporting, cite the period:
- **LTV-30:** Revenue from customers acquired in the last 30 days
- **LTV-90:** Revenue from customers acquired in the last 90 days
- **LTV-365:** Revenue from customers acquired in the last 365 days

**Source table:** `mart_customers` (dbt)

**SQL:**
```sql
-- All-time LTV per customer
select email_hash, ltv_dollars, total_orders
from mart_customers
order by ltv_dollars desc

-- LTV-30 (customers acquired in last 30 days)
select avg(ltv_dollars) as avg_ltv_30d
from mart_customers
where acquisition_date >= current_date - interval 30 day
```

**Current data availability:** ✅ All-time LTV computable. Windowed LTV computable
but **not statistically meaningful at N=5 customers**. Revisit after N ≥ 50.

**Target:** LTV > CAC × 3 (unit-economics floor); at current blended CAC of ~$146
(see below), LTV > $438 is the minimum viable threshold. The two repeat customers
(anthonypivy, awoods) are already above this bar.

**Distribution (all-time):**

```{r ltv}
tibble(
  Statistic  = c("N customers","Min LTV","Median LTV","Mean LTV","Max LTV"),
  Value      = c(
    as.character(nrow(customers)),
    dollar(min(customers$ltv_dollars)),
    dollar(median(customers$ltv_dollars)),
    dollar(mean(customers$ltv_dollars)),
    dollar(max(customers$ltv_dollars))
  )
) |>
  kable(align = c("l","r")) |>
  kable_styling(bootstrap_options = c("condensed"), full_width = FALSE)
```

**LTV by time window (windowed revenue, all customers):**

```{r ltv_windows}
windows <- tibble(
  Window       = c("LTV-30d","LTV-90d","LTV-365d"),
  `Start Date` = as.character(c(ref_date - 30, ref_date - 90, ref_date - 365)),
  `N customers in window` = NA_integer_,
  `Mean LTV`   = NA_character_
)

for (i in seq_along(c(30L, 90L, 365L))) {
  days <- c(30L, 90L, 365L)[i]
  w <- orders |>
    filter(order_date >= ref_date - days) |>
    group_by(email) |>
    summarise(ltv = sum(amount_dollars), .groups = "drop")
  windows$`N customers in window`[i] <- nrow(w)
  windows$`Mean LTV`[i] <- if (nrow(w) > 0) dollar(mean(w$ltv)) else "—"
}

windows |>
  kable(align = c("l","l","r","r")) |>
  kable_styling(bootstrap_options = c("condensed"), full_width = FALSE)
```

::: {.callout-warning}
**Small-sample caveat:** Only `r nrow(customers)` unique customers total.
All LTV statistics are dominated by high-frequency internal/test accounts.
LTV is not a stable metric until N ≥ 50 customers.
:::

---

## Order Frequency

**Business definition:** Average number of orders placed per customer per month.
Informs subscription design and re-engagement cadence. High frequency = customers
find ongoing value; low frequency = one-time buyers who need a re-purchase nudge.

**Formula:**
`total_orders / n_customers / active_months`
where `active_months = (max_order_date - first_order_date_across_cohort) / 30`.

**Source table:** `mart_customers`

**SQL:**
```sql
select
  avg(total_orders)                               as avg_orders_per_customer,
  avg(total_orders / greatest(months_active, 1))  as avg_orders_per_customer_per_month
from mart_customers
```

**Current data availability:** ✅ Computable but not statistically meaningful at N=5.

**Target:** ≥ 2 orders/customer/month (weekly box = ~4/month ceiling; bi-weekly = 2;
monthly = 1). A subscription model would lock in this frequency.

**Current values:**

```{r order_frequency}
n_months_active <- as.numeric(max(customers$last_order) - min(customers$first_order)) / 30

tibble(
  Metric = c(
    "N customers",
    "Total orders",
    "Mean orders/customer (all-time)",
    "Observation period (months)",
    "Mean orders/customer/month"
  ),
  Value = c(
    as.character(nrow(customers)),
    as.character(nrow(orders)),
    sprintf("%.1f", mean(customers$total_orders)),
    sprintf("%.1f", n_months_active),
    sprintf("%.2f", mean(customers$total_orders) / max(n_months_active, 1))
  )
) |>
  kable(align = c("l","r")) |>
  kable_styling(bootstrap_options = c("condensed"), full_width = FALSE)
```

::: {.callout-warning}
Order frequency is skewed by two high-volume accounts (likely internal/test).
Segment by `is_internal` flag once that column is added to `mart_customers`.
:::

---

## Retention Rate

**Business definition:** Fraction of customers who placed their first order in a
given cohort month and then placed at least one additional order within N days.
Answers: "Do customers come back?" Informs loyalty programs and re-engagement
email triggers.

**Formula (30-day window):**
`count(customers: first_order in cohort_month AND second_order ≤ first_order + 30d) /
count(customers: first_order in cohort_month)`

**Variants:**
- **Retention-30:** second order within 30 days of first
- **Retention-60:** second order within 60 days of first
- **Retention-90:** second order within 90 days of first

**Source table:** `mart_customers`

**SQL:**
```sql
-- Cohort retention
select
  cohort_month,
  count(*)                               as cohort_size,
  countif(days_to_second_order <= 30)    as retained_30d,
  countif(days_to_second_order <= 60)    as retained_60d,
  countif(days_to_second_order <= 90)    as retained_90d,
  countif(days_to_second_order <= 30) / count(*) as retention_30d_rate
from mart_customer_cohorts
group by cohort_month
order by cohort_month
```

**Current data availability:** ⚠️ **Partially computable.** Only `r nrow(customers)`
customers. Earliest customer acquired `r min(customers$first_order)`. Cohort-based
retention is not statistically meaningful until there are ≥ 10 customers in a
single cohort month.

**Target:** 30-day retention ≥ 40% (industry benchmark for specialty food
subscription is 35–50%). At 30 orders/week target, a 40% 30-day retention means
roughly 12 returning customers per week out of 30.

**Current values (all customers, point-in-time):**

```{r retention}
repeat_customers <- sum(customers$total_orders > 1)
total_customers  <- nrow(customers)

# Days to second order
retention_data <- orders |>
  arrange(email, order_date) |>
  group_by(email) |>
  mutate(order_rank = row_number()) |>
  filter(order_rank <= 2) |>
  summarise(
    first_order  = min(order_date),
    second_order = if (n() >= 2) max(order_date) else as.Date(NA),
    .groups      = "drop"
  ) |>
  mutate(days_to_second = as.numeric(second_order - first_order))

ret_30 <- sum(!is.na(retention_data$days_to_second) & retention_data$days_to_second <= 30)
ret_60 <- sum(!is.na(retention_data$days_to_second) & retention_data$days_to_second <= 60)
ret_90 <- sum(!is.na(retention_data$days_to_second) & retention_data$days_to_second <= 90)

tibble(
  Metric = c(
    "Total customers",
    "Customers with ≥2 orders",
    "Retention-30d (any second order within 30d of first)",
    "Retention-60d",
    "Retention-90d"
  ),
  Value = c(
    as.character(total_customers),
    as.character(repeat_customers),
    percent(ret_30 / total_customers, accuracy = 0.1),
    percent(ret_60 / total_customers, accuracy = 0.1),
    percent(ret_90 / total_customers, accuracy = 0.1)
  )
) |>
  kable(align = c("l","r")) |>
  kable_styling(bootstrap_options = c("condensed"), full_width = FALSE)
```

::: {.callout-warning}
**Interpretation:** Retention metrics are not cohort-based yet — they describe
the current universe of 5 customers, not a true month-1 cohort. Build
`mart_customer_cohorts` dbt model before quoting retention in board decks.
:::

---

## Repeat Purchase Rate

**Business definition:** Point-in-time fraction of all customers who have placed
more than one order ever. A simpler (non-cohort) variant of retention.

**Formula:** `count(customers: total_orders > 1) / count(all customers)`

**Source table:** `mart_customers`

**Current value:**

```{r repeat_rate}
n_repeat <- sum(customers$total_orders > 1)
n_total  <- nrow(customers)
tibble(
  Metric = c("Total customers","Repeat customers","Repeat rate"),
  Value  = c(
    as.character(n_total),
    as.character(n_repeat),
    percent(n_repeat / n_total, accuracy = 0.1)
  )
) |>
  kable(align = c("l","r")) |>
  kable_styling(bootstrap_options = c("condensed"), full_width = FALSE)
```

---

## Customer Acquisition (New Customers per Period)

**Business definition:** Number of distinct customers placing their first-ever order
in a given week or month. Informs whether acquisition is growing.

**Source table:** `mart_customers` (acquisition_month column)

**SQL:**
```sql
select
  acquisition_month,
  count(*) as new_customers
from mart_customers
group by acquisition_month
order by acquisition_month
```

**Current values:**

```{r acquisition}
customers |>
  mutate(acq_month = floor_date(first_order, "month")) |>
  count(acq_month) |>
  mutate(month_label = format(acq_month, "%b %Y")) |>
  select(`Acquisition Month` = month_label, `New Customers` = n) |>
  kable(align = c("l","r")) |>
  kable_styling(bootstrap_options = c("condensed"), full_width = FALSE)
```

---

# Conversion Metrics

## Full Funnel Conversion (Visit → Cart → Checkout → Purchase)

**Business definition:** The fraction of website sessions that progress through each
stage of the purchase funnel. Identifies where customers drop off, informing
UX and copy improvements.

**Formula:**
- Session → Add-to-Cart rate: `sessions_with_add_to_cart / total_sessions`
- Add-to-Cart → Begin Checkout: `sessions_with_begin_checkout / sessions_with_add_to_cart`
- Begin Checkout → Purchase: `sessions_with_purchase / sessions_with_begin_checkout`
- End-to-end CVR: `sessions_with_purchase / total_sessions`

**Source:** GA4 BigQuery export (`analytics_494626869.events_*`) or
`ga4_session_summary` parquet.

**SQL (BigQuery):**
```sql
with sessions as (
  select
    concat(user_pseudo_id, cast(ga_session_id as string)) as session_key,
    max(case when event_name = 'page_view'       then 1 end) as has_pageview,
    max(case when event_name = 'add_to_cart'     then 1 end) as has_add_to_cart,
    max(case when event_name = 'begin_checkout'  then 1 end) as has_begin_checkout,
    max(case when event_name = 'purchase'        then 1 end) as has_purchase
  from `uncle-mays-automation.analytics_494626869.events_*`
  where _table_suffix between '20260429' and format_date('%Y%m%d', current_date())
  group by session_key
)
select
  count(*)                        as total_sessions,
  sum(has_add_to_cart)            as add_to_cart_sessions,
  sum(has_begin_checkout)         as begin_checkout_sessions,
  sum(has_purchase)               as purchase_sessions,
  safe_divide(sum(has_add_to_cart),    count(*)) as visit_to_cart_rate,
  safe_divide(sum(has_begin_checkout), sum(has_add_to_cart)) as cart_to_checkout_rate,
  safe_divide(sum(has_purchase),       sum(has_begin_checkout)) as checkout_to_purchase_rate,
  safe_divide(sum(has_purchase),       count(*)) as end_to_end_cvr
from sessions
```

**Current data availability:** ⚠️ **Partial.** GA4 session parquet records 276
sessions but `add_to_cart` and `begin_checkout` event counts are all zero.
This indicates GA4 custom event tracking (add_to_cart, begin_checkout) is
**not firing** — only the native `purchase` event is captured. Full funnel
analysis requires fixing GA4 event tracking in the checkout flow.

**Baseline (available today):**

```{r funnel}
if (nrow(ga4) > 0) {
  ga4_num <- ga4 |>
    mutate(
      add_to_cart_events    = as.numeric(add_to_cart_events),
      begin_checkout_events = as.numeric(begin_checkout_events),
      purchase_events       = as.numeric(purchase_events)
    )

  n_sessions       <- nrow(ga4_num)
  n_cart           <- sum(ga4_num$add_to_cart_events > 0, na.rm = TRUE)
  n_checkout       <- sum(ga4_num$begin_checkout_events > 0, na.rm = TRUE)
  n_purchase       <- sum(ga4_num$purchase_events > 0, na.rm = TRUE)

  tibble(
    Stage  = c("Sessions","Sessions with add-to-cart","Sessions with begin-checkout","Sessions with purchase"),
    Count  = c(n_sessions, n_cart, n_checkout, n_purchase),
    `Rate vs. sessions` = c(
      "—",
      percent(n_cart     / n_sessions, accuracy = 0.1),
      percent(n_checkout / n_sessions, accuracy = 0.1),
      percent(n_purchase / n_sessions, accuracy = 0.1)
    ),
    Note = c(
      "GA4 export from 2026-04-29",
      "⚠ GA4 event not firing",
      "⚠ GA4 event not firing",
      "GA4 purchase event active"
    )
  ) |>
    kable(align = c("l","r","r","l")) |>
    kable_styling(bootstrap_options = c("condensed"), full_width = FALSE)
}
```

**Target:**
- Visit → Purchase (end-to-end CVR): ≥ 1.0% (current baseline 0.10%; industry
  median for specialty food DTC is 1–3%)
- Add-to-Cart → Purchase: ≥ 25%

**Action required:** File GA4 event tracking fix with CTO. Without this data
the funnel cannot be optimized.

---

## Checkout Conversion Rate (Stripe)

**Business definition:** Fraction of Stripe Checkout Sessions where payment was
collected. Lower-funnel metric; denominator is only sessions where the customer
reached the Stripe checkout page.

**Formula:** `count(payment_status = 'paid') / count(all sessions)`

**Source table:** `stg_stripe_checkout_sessions`

**SQL:**
```sql
select
  count(case when is_converted then 1 end)  as converted_sessions,
  count(*)                                  as total_sessions,
  avg(cast(is_converted as int)) * 100      as checkout_cvr_pct
from stg_stripe_checkout_sessions
```

**Current data availability:** ✅ Computable.

**Target:** ≥ 70% (industry norm for DTC checkout pages that the customer
voluntarily navigated to).

**Current value:**

```{r checkout_cvr}
if (nrow(cs) > 0) {
  paid  <- sum(cs$payment_status == "paid", na.rm = TRUE)
  total <- nrow(cs)
  tibble(
    Metric = c("Total sessions","Paid sessions","Checkout CVR","Abandonment rate"),
    Value  = c(
      comma(total),
      comma(paid),
      percent(paid / total, accuracy = 0.1),
      percent(1 - paid / total, accuracy = 0.1)
    )
  ) |>
    kable(align = c("l","r")) |>
    kable_styling(bootstrap_options = c("condensed"), full_width = FALSE)
}
```

::: {.callout-note}
Sessions prior to 2026-05-03 lack UTM attribution metadata. Checkout CVR by
traffic source will be available once a meaningful post-2026-05-03 dataset
accumulates.
:::

---

## Site-Wide Conversion Rate (GA4)

**Business definition:** Fraction of all GA4 sessions that resulted in a purchase.
The broadest CVR measure; reflects both traffic quality and the entire site
experience.

**Formula:** `purchase_sessions / total_sessions`

**Source:** `analytics_494626869.events_*` (BigQuery)

**SQL (BigQuery):**
```sql
select
  count(distinct session_id)                                          as sessions,
  count(distinct case when event_name = 'purchase' then session_id end)
                                                                      as purchase_sessions,
  safe_divide(
    count(distinct case when event_name = 'purchase' then session_id end),
    count(distinct session_id)
  )                                                                   as site_cvr
from `uncle-mays-automation.analytics_494626869.events_*`
where _table_suffix between '20260429' and format_date('%Y%m%d', current_date())
```

**Baseline:** 0.10% site-wide CVR (CIO audit 2026-04-29). GA4 export only
started 2026-04-29; GA4 session parquet shows 1 purchase in 276 sessions = 0.36%.

**Target:** ≥ 1.0% (10× current baseline; requires both traffic quality improvement
and funnel optimization).

---

# Marketing & Acquisition Metrics

## Customer Acquisition Cost (CAC)

**Business definition:** Total marketing spend divided by the number of new unique
customers acquired in the same period. The primary efficiency metric for paid
acquisition. Informs how much budget is justified per channel.

**Formula:** `sum(ad_spend_dollars) / count(new_customers)`

**By channel:**
- **Meta CAC:** `meta_spend / meta_attributed_new_customers`
- **Google CAC:** `google_spend / google_attributed_new_customers`
- **Blended CAC:** `(meta_spend + google_spend) / all_new_customers_in_period`
- **Organic / Direct CAC:** $0 (by definition; fixed costs only)

**Source table:** `mart_channel_performance` (dbt, to be built)

**SQL:**
```sql
select
  channel,
  sum(ad_spend_dollars)                            as spend,
  count(distinct customer_email)                   as new_customers,
  sum(ad_spend_dollars) / nullif(count(distinct customer_email), 0) as cac
from mart_channel_performance
where order_week between :start_week and :end_week
group by channel
```

**Current data availability:** ⚠️ **Partially computable from local parquet.**
Ad spend data exists locally for Meta and Google Ads (parquet at `ml/data/raw/`).
Attribution to specific customers is limited: only 6 of 34 orders have `utm_source`
populated (pre-2026-05-03 orders lack attribution). Full channel-level CAC
requires (1) post-2026-05-03 order data with UTM attribution, and (2) `mart_channel_performance`
dbt model.

**Blended CAC (current estimate — paid period only):**

```{r cac}
if (nrow(meta) > 0 && nrow(gads) > 0) {
  meta_spend  <- sum(meta$spend_usd, na.rm = TRUE)
  gads_spend  <- sum(gads$spend_usd, na.rm = TRUE)
  total_spend <- meta_spend + gads_spend

  # Orders placed after ad campaign start (2026-04-24)
  ad_start    <- as.Date("2026-04-24")
  paid_orders <- orders |> filter(order_date >= ad_start)
  new_custs   <- paid_orders |>
    semi_join(
      customers |> filter(first_order >= ad_start),
      by = "email"
    ) |>
    pull(email) |> n_distinct()

  tibble(
    Metric = c(
      "Meta spend (Apr 24 – May 2)",
      "Google spend (Apr 24 – May 2)",
      "Total paid spend",
      "Orders in paid period",
      "New customers in paid period",
      "Blended CAC (total spend / new customers)"
    ),
    Value = c(
      dollar(meta_spend),
      dollar(gads_spend),
      dollar(total_spend),
      as.character(nrow(paid_orders)),
      as.character(new_custs),
      if (new_custs > 0) dollar(total_spend / new_custs) else "—"
    )
  ) |>
    kable(align = c("l","r")) |>
    kable_styling(bootstrap_options = c("condensed"), full_width = FALSE)
}
```

**Target:**
- Blended CAC ≤ LTV / 3 (unit economics floor).
- At target LTV ~$200 (assuming 3 orders × $65 AOV), maximum CAC = $67.
- Current blended CAC of ~$146 is above this threshold — the business is
  currently acquiring customers at a loss on paid channels. Paid spend should
  be paused or restructured until CAC improves (requires board approval per
  standing order).

---

## Return on Ad Spend (ROAS)

**Business definition:** Gross revenue generated per dollar of ad spend.
ROAS > 1 means the channel generates more revenue than it costs (before COGS).

**Formula:** `sum(gross_revenue_dollars) / sum(ad_spend_dollars)`

**Note:** ROAS alone does not indicate profitability — subtract COGS and
fulfillment costs for contribution margin ROAS.

**Source table:** `mart_channel_performance` (dbt)

```{r roas}
if (nrow(meta) > 0 && nrow(gads) > 0) {
  ad_start    <- as.Date("2026-04-24")
  paid_rev    <- sum(orders$amount_dollars[orders$order_date >= ad_start])
  total_spend <- sum(meta$spend_usd) + sum(gads$spend_usd)

  tibble(
    Metric = c("Paid-period revenue","Total paid spend","Blended ROAS"),
    Value  = c(
      dollar(paid_rev),
      dollar(total_spend),
      sprintf("%.2f×", paid_rev / total_spend)
    )
  ) |>
    kable(align = c("l","r")) |>
    kable_styling(bootstrap_options = c("condensed"), full_width = FALSE)
}
```

**Target:** ROAS ≥ 3× (covers COGS + gross margin at 33% margin assumption).

---

# Financial Metrics

## Gross Margin

**Business definition:** (Gross Revenue − Cost of Goods Sold) / Gross Revenue.
Measures how much of each revenue dollar remains after paying for the produce.

**Formula:** `(revenue - cogs) / revenue`

**Source table:** `mart_sku_margin` (not yet built)

**Current data availability:** ⚠️ **Not computable.** COGS requires:
1. Vendor cost per SKU — not yet in Airtable Catalog table
2. SKU quantity per order — requires consistent `cart_json` capture

**Action required:** COO to add vendor cost column to Airtable Catalog.
Data Engineer to ensure `cart_json` is populated for every order.

**Target:** Gross margin ≥ 35% (specialty produce DTC typical range: 30–45%).

---

## Contribution Margin per SKU

**Business definition:** Per-unit revenue minus per-unit variable cost, expressed
as a percentage of revenue. Identifies which SKUs actually contribute to profit
and which should be repriced or dropped.

**Formula:** `(unit_price - unit_variable_cost) / unit_price`

**Source table:** `mart_sku_margin` (not yet built)

**Current data availability:** ⚠️ **Not computable.** Same blockers as Gross Margin.
Customer-facing prices are in Airtable (`appm6F6H9obydzAM2`, table `Catalog`,
45 active SKUs). Vendor costs are missing.

---

# Data Quality & Coverage Summary

| Metric | Status | Computable Today? | Key Blocker |
|--------|--------|-------------------|-------------|
| AOV (total) | ✅ Live | Yes | — |
| AOV by SKU category | ⚠️ Partial | No | `cart_json` inconsistent |
| Weekly Revenue | ✅ Live | Yes | — |
| LTV (all-time) | ✅ Live | Yes | N too small for inference |
| LTV (30/90/365-day) | ✅ Live | Yes | N too small for inference |
| Order Frequency | ✅ Live | Yes | N too small for inference |
| Retention Rate (30/60/90d) | ⚠️ Partial | Point-in-time only | Need cohort model |
| Repeat Purchase Rate | ✅ Live | Yes | — |
| Checkout CVR (Stripe) | ✅ Live | Yes | — |
| Full Funnel CVR (GA4) | ⚠️ Partial | Partial | GA4 events not firing |
| Site-wide CVR | ✅ Live | Yes | Short history (from Apr 29) |
| CAC (blended) | ✅ Live | Yes (estimate) | UTM attribution sparse pre-May 3 |
| CAC (by channel) | ⚠️ Pending | No | `mart_channel_performance` not built |
| ROAS | ⚠️ Pending | Blended only | Channel attribution needed |
| Gross Margin | ❌ Blocked | No | Vendor costs missing from Airtable |
| Contribution Margin/SKU | ❌ Blocked | No | Same as Gross Margin |

---

# Data Source Freshness

| Source | Last Ingested | Known Issues |
|--------|--------------|--------------|
| Stripe PaymentIntents | 2026-05-02 | UTM/fbclid/gclid null before 2026-05-03 |
| Stripe CheckoutSessions | 2026-05-02 | Most sessions unpaid (checkout page opens ≠ intent to buy) |
| GA4 BigQuery export | Daily from 2026-04-29 | `add_to_cart` / `begin_checkout` events not firing |
| Meta Ads | 2026-05-02 | Local parquet only; not yet in BigQuery |
| Google Ads | 2026-05-02 | Local parquet only; not yet in BigQuery |
| Mailchimp | 2026-05-02 | Not yet joined to orders |
| Airtable Catalog | Live (API) | 45 active SKUs; vendor cost column missing |

---

# Appendix: Metric Ownership

| Metric | dbt Model | Status | Owner | Last Reviewed |
|--------|-----------|--------|-------|---------------|
| AOV | mart_orders | Live | Analytics Engineer | 2026-05-03 |
| Weekly Revenue | mart_orders | Live | Analytics Engineer | 2026-05-03 |
| All-time Revenue | mart_orders | Live | Analytics Engineer | 2026-05-03 |
| Customer LTV | mart_customers | Live | Analytics Engineer | 2026-05-03 |
| Order Frequency | mart_customers | Live | Analytics Engineer | 2026-05-03 |
| Retention Rate | mart_customer_cohorts (pending) | Partial | Analytics Engineer | 2026-05-03 |
| Repeat Purchase Rate | mart_customers | Live | Analytics Engineer | 2026-05-03 |
| Checkout CVR | stg_stripe_checkout_sessions | Live | Analytics Engineer | 2026-05-03 |
| Full Funnel CVR | GA4 BQ (events broken) | Partial | Analytics Engineer | 2026-05-03 |
| Site-wide CVR | GA4 BQ direct | Live (BQ only) | Analytics Engineer | 2026-05-03 |
| CAC (blended) | mart_channel_performance (pending) | Estimate from parquet | Analytics Engineer | 2026-05-03 |
| CAC (by channel) | mart_channel_performance (pending) | Pending model build | Analytics Engineer | — |
| ROAS | mart_channel_performance (pending) | Partial | Analytics Engineer | 2026-05-03 |
| Gross Margin | mart_sku_margin (not built) | Blocked on COGS data | Analytics Engineer | — |
| Contribution Margin/SKU | mart_sku_margin (not built) | Blocked on COGS data | Analytics Engineer | — |
